---
title: "Homework 6"
author: "Paula Wu"
date: "11/23/2021"
output: github_document
---
Import the libraries
```{r, message=FALSE}
library(tidyverse)
library(viridis)
library(modelr)
library(patchwork)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

## Problem 1
#### Data Preprocessing
Read in data and data cleaning
```{r, message = FALSE}
birth_weight_df = read_csv("./data/birthweight.csv") %>% 
  janitor::clean_names() %>% 
  mutate(babysex = as.factor(babysex),
         malform = as.factor(malform),
         frace = as.factor(frace),
         mrace = as.factor(mrace))
knitr::kable(birth_weight_df[1:7,])
```

Check for missing values
```{r}
birth_weight_df %>% 
  select(everything()) %>%  
  summarise_all(funs(sum(is.na(.)))) %>% 
  knitr::kable()
```
As we can see from above, no missing values appeared in the data set. Thus, no imputation is needed. <br>

#### Regression
**My proposed model**:<br>
I did some research on potential factors that could affect infants' birth weights: "Low birth weight is associated with many socio-economic factors such as residence, mother's age and occupation, birth order, the family's income and many maternal conditions such as nutritional status, mother's educational and health status [1]." <br><br>

Thus, I proposed my model to explore the associations among: `fincome` (family income), `momage` (mother's age at delivery), `parity`(to approximate birth order), `smoken` and `ppbmi` (to approximate maternal conditions).
```{r}
my_model_fit = lm(bwt ~ fincome + momage + parity + smoken + ppbmi, data = birth_weight_df)
broom::tidy(my_model_fit)
```
Plot residual plots
```{r}
birth_weight_df %>% 
  modelr::add_residuals(my_model_fit) %>%
  modelr::add_predictions(my_model_fit) %>% 
  ggplot(aes(x = pred, y = resid))+
  geom_point(aes(alpha = 0.5))+
  geom_smooth(se = FALSE, method = lm, color = "red")
```
**Compared to other two models**:<br>
First model: using length at birth and gestational age as predictors (main effects only)
```{r}
f_model_fit = lm(bwt ~ blength + gaweeks, data = birth_weight_df) 
broom::tidy(f_model_fit)
```

Second model:using head circumference, length, sex, and all interactions (including the three-way interaction) between these
```{r}
s_model_fit = lm(bwt ~ bhead + blength + babysex + bhead*blength 
                 + bhead*babysex + blength*babysex + bhead*blength*babysex, 
                 data = birth_weight_df)
broom::tidy(s_model_fit)
```

```{r}
cv_df = 
  crossv_mc(birth_weight_df,100) %>% 
  mutate(
    train = map(train, as_tibble),  # transform to tibble
    test = map(test, as_tibble)
  )
cv_df = 
  cv_df %>% 
  mutate(
    my_model_fit = map(.x = train, ~lm(bwt ~ fincome + momage + parity + smoken + ppbmi, data = .x)),
    f_model_fit = map(.x = train, ~lm(bwt ~ blength + gaweeks, data = .x) ),
    s_model_fit = map(.x = train, ~lm(bwt ~ bhead + blength + babysex + bhead*blength 
                 + bhead*babysex + blength*babysex + bhead*blength*babysex, 
                 data = .x))
  ) %>% 
  mutate(
    rmse_my = map2_dbl(.x = my_model_fit, .y = test, ~rmse(model = .x, data = .y)),
    rmse_f_model = map2_dbl(.x = f_model_fit, .y = test, ~rmse(model = .x, data = .y)),
    rmse_s_model = map2_dbl(.x = s_model_fit, .y = test, ~rmse(model = .x, data = .y))
  )
```

Look at the results
```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  mutate(model = fct_relevel(model, "my", "f_model", "s_model")) %>% 
  ggplot(aes(x = model, y = rmse,))+
  geom_boxplot(aes(fill = model, alpha = 0.3))+
  theme(legend.position = "none")
```





## Problem 2
Load in the data, codes copied from homework website
```{r, message=FALSE, warning=FALSE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```
Set the seed to ensure I can get the same results each time I ran my code
```{r}
set.seed(1) 
```

### R-squared
```{r}
r_squared_results = 
  weather_df %>% 
  bootstrap(n = 5000, id = "strap_number") %>% 
  mutate(
    models = map(.x = strap, ~lm(tmax~tmin, data = .x)),
    results = map(models, broom::glance)
  ) %>% 
  select(-models, -strap) %>% 
  unnest(results) %>% 
  janitor::clean_names()  # the variable names are not that cleaned
r_squared_results %>% 
  summarize(
    ci_lower = quantile(r_squared, 0.025),
    ci_upper = quantile(r_squared, 0.975)
  )
```
#### log(beta_0 * beta_1)
```{r}
log_beta_results = 
  weather_df %>% 
  bootstrap(n = 5000, id = "strap_number") %>% 
  mutate(
    models = map(.x = strap, ~lm(tmax~tmin, data = .x)),
    results = map(models, broom::tidy)
  ) %>% 
  select(-models, -strap) %>% 
  unnest(results) %>% 
  select(strap_number, term, estimate) %>% 
  pivot_wider(names_from = term, values_from = estimate) %>% 
  janitor::clean_names() %>% 
  mutate(log_beta_zo = log(intercept*tmin))

log_beta_results %>% 
  summarize(
    ci_lower = quantile(log_beta_zo, 0.025),
    ci_upper = quantile(log_beta_zo, 0.975)
  )
```
#### Plots
```{r}
# r squared
r_squared_results %>% 
  ggplot(aes(x = r_squared))+  # plot the estimate
  geom_density()
```
```{r}
log_beta_results %>% 
  ggplot(aes(x = log_beta_zo))+  # plot the estimate
  geom_density() 
```




## Reference
[1] Maternal Associated Factors of Low Birth Weight
